---
title: "Data Acquisition"
author: "Davis Rakhshan"
---

# Challenge 1

Question 1:

Get some data via an API. There are millions of providers, that offer API access for free and have good documentation about how to query their service. You just have to google them. You can use whatever service you want. For example, you can get data about your listening history (spotify), get data about flights (skyscanner) or just check the weather forecast. Print the data in a readable format, e.g. a table if you want, you could also plot it.

Code:

```{r}
library(RSQLite)
library(httr)
library(glue)
library(jsonlite)
library("tidyverse")
library(rvest)

# Challenge 1

# Latitude and longitude of TUHH
latitude <- "53.46"
longitude <- "9.97"
  
resp <- GET(glue("https://api.open-meteo.com/v1/forecast?latitude={latitude}&longitude={longitude}&hourly=temperature_2m&timezone=Europe%2FBerlin"))

respTable <- resp %>% 
            .$content %>% 
            rawToChar() %>% 
            fromJSON()
respTable


# Extract relevant data from the response
forecast_data <- respTable$hourly

# Create a tibble
weather_tbl <- tibble(
  time = forecast_data$time,
  temperature_2m = forecast_data$temperature_2m
)

# Print the tibble
print(weather_tbl)



# Convert time to datetime format
weather_tbl$time <- as.POSIXct(weather_tbl$time, format = "%Y-%m-%dT%H:%M")

# Ensure data is sorted by time
weather_tbl <- weather_tbl %>% arrange(time)


# Extract day part of the date
weather_tbl$day <- factor(format(weather_tbl$time, "%d"), levels = unique(format(weather_tbl$time, "%d")))
weather_tbl <- na.omit(weather_tbl)


# Create a plot
p <- ggplot(weather_tbl, aes(x = time, y = temperature_2m)) +
  geom_point(position = "identity") +  # Set position to "identity" to remove space between points
  geom_line(color = "blue", show.legend = FALSE) +
  labs(title = "Hourly Temperature for 7 Days",
       subtitle = "Ordered by date and time",
       x = "Time",
       y = "Temperature (°C)") +
  theme_minimal() +
  facet_wrap(~ factor(format(weather_tbl$time, "%A"), levels = unique(format(weather_tbl$time, "%A"))), nrow = 1, scales = "free_x")

# Adjust x-axis labels to show only time with ":00"
p <- p + scale_x_datetime(date_breaks = "6 hours", date_labels = "%H:%M:00") # Adjust date_labels

# Remove space between plots
p <- p + theme(strip.text = element_text(size = 8, face = "bold"), 
               panel.spacing = unit(0, "lines"),
               axis.text.x = element_text(angle = 45, hjust = 1, size = 8), # Adjust angle and size
               legend.title = element_blank())

# Print the plot
print(p)
```

# Challenge 2

Question 2:

Scrape one of the competitor websites of canyon (either https://www.rosebikes.de/ or https://www.radon-bikes.de) and create a small database. The database should contain the model names and prices for at least one category. Use the selectorgadget to get a good understanding of the website structure, it is really helpful. After scraping your data, convert it to a readable format. Prices should be in a numeric format without any other letters or symbols. Also check if the prices are reasonable.

Code:

```{r}

# Challenge 2

# Define the URL of the website
url_race <- "https://www.rosebikes.de/fahrr%C3%A4der/rennrad/race"
url_endurance <- "https://www.rosebikes.de/fahrr%C3%A4der/rennrad/endurance"
url_eBike <- "https://www.rosebikes.de/fahrr%C3%A4der/rennrad/e-rennrad"

# Read the HTML content of the webpage
webpage_race <- url_race %>% read_html()
webpage_endurance <- url_endurance %>% read_html()
webpage_eBike <- url_eBike %>% read_html()

# Extract the content within the h4 tag with class "basic-headline__title"
title_race        <- html_text(html_nodes(webpage_race, "h4.basic-headline__title"))
title_endurance   <- html_text(html_nodes(webpage_endurance, "h4.basic-headline__title"))
title_eBike       <- html_text(html_nodes(webpage_eBike, "h4.basic-headline__title"))

# Extract the content within the specified class "catalog-category-bikes__price-title"
price_title_race      <- html_text(html_nodes(webpage_race, ".catalog-category-bikes__price-title"))
price_title_endurance <- html_text(html_nodes(webpage_endurance, ".catalog-category-bikes__price-title"))
price_title_eBike<- html_text(html_nodes(webpage_eBike, ".catalog-category-bikes__price-title"))

# Remove "ab " and "\n" from the price
price_title_race <- gsub("ab |\\n", "", price_title_race)
price_title_endurance <- gsub("ab |\\n", "", price_title_endurance)
price_title_eBike<- gsub("ab |\\n", "", price_title_eBike)

# Remove trailing whitespaces
price_title_race <- trimws(price_title_race)
price_title_endurance <- trimws(price_title_endurance)
price_title_eBike<- trimws(price_title_eBike)


# Create a tibble with the extracted content
bike_data_race <- tibble(model = title_race, price = price_title_race)
bike_data_endurance <- tibble(model = title_endurance, price = price_title_endurance)
bike_data_eBike<- tibble(model = title_eBike, price = price_title_eBike)


# Print the tibble
print(bike_data_race)
print(bike_data_endurance)
print(bike_data_eBike)
```
